Donor Responses to Civil Society Repression

### 2024-11-05 README.qmd
oops, get metadata from actual manuscript

yaml_metadata <- rmarkdown::yaml_front_matter("manuscript.qmd")
title <- yaml_metadata$title
# abstract <- yaml_metadata$abstract
abstract <- "Given the increase in administrative and legal repression of civil society, how have their donors responded? How do these responses differ across foreign government and private donors? How have local philanthropists and NGOs adapted and responded to such repression? What challenges do civil society groups continue to face despite these responses?"
```

>>>>

yaml_metadata <- rmarkdown::yaml_front_matter("index.qmd")
title <- yaml_metadata$title
# abstract <- yaml_metadata$abstract
abstract <- "Given the increase in administrative and legal repression of civil society, how have their donors responded? How do these responses differ across foreign government and private donors? How have local philanthropists and NGOs adapted and responded to such repression? What challenges do civil society groups continue to face despite these responses?"
```
